A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-02 src/paper.tex
Changes in structure
WIP: Application hosting infrastructure

@@

The second screen devices and iTV terminals have client applications that consume the web services in order to present the content to the viewers. These client applications also use the web services as an interface to send interaction data to the CP. Since applications in the TV domain have the potential to reach out millions of users at the same time, it is interesting to consider the use of a cloud based platform in the CP infrastructure~\cite{Lee2010}.

% descrever a possibilidade de autenticação em outra arte do texto: A possible way to do so is to generate a registration code for each equipment

@@

\subsection{Web Services Design}

- RESTful API

- Resources

@@

@@

@@

\subsection{RESTful API}

>>>>

The sections of this paper are arranged as follows: \ldots

@@

The second screen devices and iTV terminals have client applications that consume the web services in order to present the content to the viewers. These client applications also use the web services as an interface to send interaction data to the CP.

% descrever a possibilidade de autenticação em outra parte do texto: A possible way to do so is to generate a registration code for each equipment

@@

\subsection{Application Hosting Infrastructure}

Since applications in the TV domain have the potential to reach out millions of users at the same time, it is interesting to consider the use of a cloud based platform for storing and processing data~\cite{Lee2010}.

The front controller architectural design pattern~\cite{Buschmann2007} is employed to centralize requests processing in a single component. Each second screen client sends requests to and receives responses from a single URL, what simplifies application development.

- Web application

@@

- presence detector

@@

- web services Consumption

- web services usage

@@

\subsection{RESTful API Design and Implementation}
